Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{float}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

%need to fix formatting
\begin{tabular}{ |p{2cm}||p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
  \hline
  \multicolumn{9}{|c|}{Summary} \\
  \hline
  Variable & Min. & 1st Quantile & Median & Mean & 3rd Quantile & Max. \\
  \hline
  TPEC & 5.669 & 6.07& 7.609 & 7.462 & 8.082 & 9.965\\
  GDP &  1377 & 4341 & 8363 & 9962 & 14940 & 25248\\
  POP & 211192 & 238482 & 271709 & 273195 & 30886 & 332940\\
  TCMR & .6506 & 3.4607 & 6.1448 & 6.1156 & 8.054 & 14.8384\\
  DPI & 968.7 & 3114.2 & 6037.2 & 7440.5 & 11171.3 & 19586.5\\
  UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96\\
  \hline
\end{tabular}

@@

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{setspace}
\usepackage{float}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

\begin{tabular}{ |p{2cm}||p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}| }
  \hline
  \multicolumn{7}{|c|}{Summary} \\
  \hline
  Variable & Min. & 1st Q & Median & Mean & 3rd Q & Max. \\
  \hline
  TPEC & 5.669 & 6.07& 7.609 & 7.462 & 8.082 & 9.965\\
  GDP &  1377 & 4341 & 8363 & 9962 & 14940 & 25248\\
  POP & 211192 & 238482 & 271709 & 273195 & 30886 & 332940\\
  TCMR & .6506 & 3.4607 & 6.1448 & 6.1156 & 8.054 & 14.8384\\
  DPI & 968.7 & 3114.2 & 6037.2 & 7440.5 & 11171.3 & 19586.5\\
  UNRATE & 3.6 & 5.05 & 5.867 & 6.231 & 7.3 & 12.967\\
  BSPL & 45.99 & 56.35 & 67.69 & 75.44 & 98.96 & 116.10\\
  \hline
\end{tabular}

@@

From the output produced in the Added-Variable Plots from Model 2, it confirms there is a strong linear relationship between the variables TCMR, DPI, UNRATE and BSLP with GDP.
